EldersAIR initial Micropem data work

### 2020-09-10 micropem_data_cleaning.Rmd
new micropem data cleaning

---
title: "EldersAIR initial Micropem data work"
author: "Ethan Walker"
date: "Started 2 March 2020, Updated 31 Aug 2020"
output: pdf_document
---

@@

# Change function input to look at specific home
# Run all of these lines together
pm_time_plot_function(id = "65", location = "NPT", visit = 1)
head(gaps, 10)
head(pm_desc, 10)
tail(pm_desc, 10)

@@

>>>>

---
title: "EldersAIR initial Micropem data work"
author: "Ethan Walker"
date: "Started 2 March 2020, Updated 4 Sept 2020"
output: pdf_document
---

@@

# Change function input to look at specific home
# Run all of these lines together
pm_time_plot_function(id = "210", location = "NPT", visit = 2)
head(gaps, 10)
head(pm_desc, 10)
tail(pm_desc, 10)

@@

# Further cleaning steps after checking individual files
```{r}
# load data
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/EldersAIR/")

npt_micropem_new <- npt_micropem %>% 
  group_by(mp_file_name) %>% 
  mutate(pm_personal_new = if_else(pm_personal < 0, 0, pm_personal),
         pm_mean_new = mean(pm_personal_new, na.rm = TRUE),
         pm_diff = round(pm_mean_new - pm_mean, digits = 2),
         pm_diff_perc = round(abs(pm_diff/pm_mean*100), digits = 2),
         pm_indicator = if_else(pm_diff_perc > 5 & pm_diff > 2, 1, 0)) %>% 
  ungroup() %>% 
  distinct(mp_file_name, .keep_all = TRUE) %>% 
  select(mp_file_name, area, home, home_winter_id, sampling_visit,
         pm_mean, pm_mean_new, pm_diff, pm_diff_perc, pm_indicator) %>% 
  filter(pm_indicator == 1)
```
